### 2022-04-04 papers.tex
Mostly finalized tracks

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Tell next year's committee that they should probably avoid further milking of the blindsight joke}

@@

\addpaper
    {Tironiculum: Latin Speech Recognition via Latin Text-to-Speech}
    {Lee Butterman}
    {Keywords: Latin, Automatic speech recognition, AI, Machine Learning, Abundant citations, Life advice, State of the Art, Competition winner, Metagaming a competition}
    {SIGBOVIK_2022_paper_0950}
    {0cm}
    {}
\addpaper
    {Abecedarial Acrostic, Alphabetized Amusingly Because Beings Blissfully Cause Celebratory Centennials... (Note: Full Title is Longer)}
    {Jacob Weiner}
    {Keywords: Records, Useless, Alphabet, Gibberish}
    {SIGBOVIK_2022_paper_1598}
    {0cm}
    {}

@@

@@

\addpaper
    {On the Possibilities and Challenges of Organic UAV-Assisted MEC}
    {S. Wallow, Cardi Nalle, Robin, P. Cock, and Sky Lark}
    {Keywords:chick-a-dee, caw caw, chirp chirp, hoot hoot}
    {SIGBOVIK_2022_paper_9501}
    {0cm}
    {}
\addtrack
    {}{Aesthetics}

@@

\addpaper
    {(Un)helper functions}
    {Kevin Smith and Bernhard Egger}
    {Keywords: algorithms, algorithm patent trolling, cite us please!}
    {SIGBOVIK_2022_paper_2133}
    {0cm}
    {}

\addtrack
    {}{Mathematics}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}
\addpaper
    {SEGA-NVidia 32esque Advertisements}
    {Jim McCann}
    {Keywords: sega, nvidia, 3D 3D, rtesque}
    {SIGBOVIK_2022_paper_6593}
    {0cm}
    {}

\addtrack{}{A Brief Musical Interlude}
%\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    {Baby Sharks are More than Sharks . They are Earworms Sung More than Happy Birthday Perhaps}
    {Kofi Oduro}
    {Keywords: Sharks, Happy Birthday, Swimming Shark Problem, Shark Week, billions, humans, kindergarten, PRe-K}
    {SIGBOVIK_2022_paper_6744}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addtrack
    {}{Construction}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}
\addpaper
    {Destructive Logic}
    {Runming Li}
    {Keywords: logic, constructive logic, destructive logic, type theory}
    {SIGBOVIK_2022_paper_6801}
    {0cm}
    {}

\addpaper
    {On Ruinment: Ruination Theory and its Consequents}
    {Luna Tascheter}
    {Ruination Theory, Ruinment, T0T4L PWN4G∃, Category Theory, Adam Conover, Adam Sandler, Hallmark, Waste of Paper, Orange}
    {SIGBOVIK_2022_paper_6808}
    {0cm}
    {}
\addtrack
    {}{Spoops}

@@

\addtrack
    {}{Uhhhh etcetera}

\addpaper
    {A sometimes-accurate O(1) search algorithm}
    {A College Freshman}
    {Keywords:fast, search, search algorithm, searching algorithm, searching, how many ways can i say search algorithm}
    {SIGBOVIK_2022_paper_4297}
    {0cm}
    {}

\addpaper
    {Edward, edMUnD & Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}

@@

\addpaper
    {Functorial wrappers for high-dimensional classification algorithms}
    {James Carzon}
    {Keywords: forgetful functor, classification, high dimensional data}
    {SIGBOVIK_2022_paper_7603}
    {0cm}
    {}
\addpaper
    {Overlap-Maximal Graph Labelings: Graph Labelings with Non-Disjoint Vertex and Edge Sets (and how they can be used for encryption, poetry, and breaking mathematics)}
    {Gabriel Chuang}
    {Keywords: Graph Theory, Cryptography, Fox in Socks by Dr. Seuss}
    {SIGBOVIK_2022_paper_6809}
    {0cm}
    {}
\addpaper
    {Analysis of A New Error Calculation Technique}
    {Jevin Tong} 
    {Keywords: late, erroneous, hackneyed}
    {SIGBOVIK_2022_paper_7011}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Tell next year's committee that they should probably avoid further milking the blindsight joke}

@@

\addpaper
    {Tironiculum: Latin Speech Recognition via Latin Text-to-Speech}
    {Lee Butterman}
    {Keywords: Latin, Automatic speech recognition, AI, Machine Learning, Abundant citations, Life advice, State of the Art, Competition winner, Metagaming a competition}
    {SIGBOVIK_2022_paper_0950}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Abecedarial Acrostic, Alphabetized Amusingly Because Beings Blissfully Cause Celebratory Centennials... (Note: Full Title is Longer)}
    {Jacob Weiner}
    {Keywords: Records, Useless, Alphabet, Gibberish}
    {SIGBOVIK_2022_paper_1598}
    {0cm}
    {}

@@

\addtrack
    {}{Systems}

\addpaper
    {Edward, edMUnD \& Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}
\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}

\addtrack
    {}{Theory}
\addpaper
    {Destructive Logic}
    {Runming Li}
    {Keywords: logic, constructive logic, destructive logic, type theory}
    {SIGBOVIK_2022_paper_6801}
    {0cm}
    {}
\addpaper
    {Overlap-Maximal Graph Labelings: Graph Labelings with Non-Disjoint Vertex and Edge Sets (and how they can be used for encryption, poetry, and breaking mathematics)}
    {Gabriel Chuang}
    {Keywords: Graph Theory, Cryptography, Fox in Socks by Dr. Seuss}
    {SIGBOVIK_2022_paper_6809}
    {0cm}
    {}

\addpaper
    {On Ruinment: Ruination Theory and its Consequents}
    {Luna Tascheter}
    {Ruination Theory, Ruinment, T0T4L PWN4G∃, Category Theory, Adam Conover, Adam Sandler, Hallmark, Waste of Paper, Orange}
    {SIGBOVIK_2022_paper_6808}
    {0cm}
    {}

@@

\addpaper
    {On the Possibilities and Challenges of Organic UAV-Assisted MEC}
    {S. Wallow, Cardi Nalle, Robin, P. Cock, and Sky Lark}
    {Keywords:chick-a-dee, caw caw, chirp chirp, hoot hoot}
    {SIGBOVIK_2022_paper_9501}
    {0cm}
    {}

\addtrack{}{A Brief Musical Interlude}
%\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    {Baby Sharks are More than Sharks . They are Earworms Sung More than Happy Birthday Perhaps}
    {Kofi Oduro}
    {Keywords: Sharks, Happy Birthday, Swimming Shark Problem, Shark Week, billions, humans, kindergarten, PRe-K}
    {SIGBOVIK_2022_paper_6744}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addtrack
    {}{Algorithmic Advances}

\addpaper
    {Functorial wrappers for high-dimensional classification algorithms}
    {James Carzon}
    {Keywords: forgetful functor, classification, high dimensional data}
    {SIGBOVIK_2022_paper_7603}
    {0cm}
    {}

\addpaper
    {(Un)helper functions}
    {Kevin Smith and Bernhard Egger}
    {Keywords: algorithms, algorithm patent trolling, cite us please!}
    {SIGBOVIK_2022_paper_2133}
    {0cm}
    {}
\addpaper
    {A sometimes-accurate O(1) search algorithm}
    {A College Freshman}
    {Keywords:fast, search, search algorithm, searching algorithm, searching, how many ways can i say search algorithm}
    {SIGBOVIK_2022_paper_4297}
    {0cm}
    {}

\addtrack
    {}{Mathematic Retreats}

\addtrack
    {}{Aesthetics}

@@

\addreview
    {SIGBOVIK_2022_review_2}
    {0cm}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}
\addtrack
    {}{Black Boxes}

@@

\addreview
    {SIGBOVIK_2022_review_1}
    {0cm}
\addtrack{}{SIGBOVIK}

\addpaper
    {Analysis of A New Error Calculation Technique}
    {Jevin Tong} 
    {Keywords: late, erroneous, hackneyed}
    {SIGBOVIK_2022_paper_7011}
    {0cm}
    {\badges{\badge{pagenumbers}}}

@@
